\section*{3. Angular size}

a) The Berliner Fernsehturm is 368 m tall. If you are standing 10 km from the tower, what is it's angular
size measured from your vantage point? Express the result in radians, degree, arcminutes, and in the form
"x degrees + y arcminutes + z arcseconds" where x, y, z are integer numbers.\\
\\
First we calculate the hypotenuse, since there is a right angle between the Fernsehturm and my distance
to the Fernsehturm.
\begin{equation*}
    \begin{split}
        a^2 + b^2 &= c^2\\
        \sqrt{a^2 + b^2} &= c\\
        \sqrt{(368 \text{ m})^2 + (10000 \text{ m})^2} &= c\\
        \sqrt{135424 \text{ m}^2 + 100000000 \text{ m}^2} &= c\\
        \sqrt{100135424 \text{ m}^2} &= c\\
        10006.7689 \text{ m} &\approx c\\
    \end{split}
\end{equation*}
Now we can calculate the angle $\alpha$ between the distance from me to the Fernsehturm and the distance 
from me to the top of the Fernsehturm $d_u$ with the height of the Fernsehturm $h$.
\begin{equation*}
    \begin{split}
        \alpha &= arcsin \biggl(\frac{\text{countercathete}}{\text{hypotenuse}}\biggr)\\
        &= arcsin \biggl(\frac{h}{d_u}\biggr)\\
        &= arcsin \biggl(\frac{368}{10006.7689}\biggr)\\
        &\approx 0.0367834015\\
        &= 2.108 \degree\\
        &= (2.108 \cdot 60)' = 126.48'\\
        &= (2.108 \cdot 3600)'' = 7588.8''\\
        &\approx 2 \degree \: 6' \: 29''\\
    \end{split}
\end{equation*}
b) Measure the length of your hand, the length of your arm, and calculate the angular size of your hand
when you stretch out your arm. Express the result in radians and degrees. Is it larger or smaller than the
angular size that you calculated in part a)?\\
\\
I measured a length of 67 cm for my arm and a length of 18.5 cm for my hand. First we calculate the
hypotenuse again.
\begin{equation*}
    \begin{split}
        a^2 + b^2 &= c^2\\
        \sqrt{a^2 + b^2} &= c\\
        \sqrt{(67 \text{ cm})^2 + (18.5 \text{ cm})^2} &= c\\
        \sqrt{4489 \text{ cm}^2 + 342.25 \text{ cm}^2} &= c\\
        \sqrt{4831.25 \text{ cm}^2} &= c\\
        69.5072 &\approx c\\
    \end{split}
\end{equation*}
Now we calculate the angle $\alpha$ like in the previous exercise.
\begin{equation*}
    \begin{split}
        \alpha &= arcsin \biggl(\frac{\text{countercathete}}{\text{hypotenuse}}\biggr)\\
        &= arcsin \biggl(\frac{h}{d_u}\biggr)\\
        &= arcsin \biggl(\frac{18.5}{69.5072}\biggr)\\
        &\approx 0.269407\\
        &= 15.44 \degree\\
    \end{split}
\end{equation*}
The angular size of my hand and arm is larger then the angular size from exercise a).
